SIR Model With Testing Flows and Isolation

### 2020-10-27 codes/ali_test_sir.Rmd
update dimensions for contour plots

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
 # specify the ranges
 beta  <- 0.4  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=5)
 eta_t <- seq(0.001,0.5, length.out=5) #0.001 to 0.5 
 rho     <- seq(0,0.01, length.out=10)
 omega <- seq(0.001,1 , length.out=10) #note omega must be > rho, was 0.1

@@

```{r contour_R0_2, message=FALSE,warning=FALSE }
 # specify the ranges
 beta  <- 0.4  
 # eta_w <- seq(0,1, length.out=5) 
 eta_t <- seq(0.001,0.5, length.out=5) #0.001 
 rho     <- seq(0,0.01, length.out=5)
 omega <- seq(0.001,1 , length.out=10) #note omega must be > 0, was 0.1
s <- seq(1,2,length.out=5)

>>>>

### Contour plot of $R_0=1$ and interpretations approache 1
```{r contour_R0_1, message=FALSE,warning=FALSE }
n_out <- 5 ## facets (rows/cols)
n_in <- 41 ## grid N within facets
 # specify the ranges
 beta  <- 0.4  ## set beta high enough to allow R0>1 in worst case
 eta_w <- seq(0,1, length.out=n_out)
 eta_t <- seq(0.001,0.5, length.out=n_out) #0.001 to 0.5 
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.001,1 , length.out=n_in) #note omega must be > rho, was 0.1

@@

```{r contour_R0_2, message=FALSE,warning=FALSE }
 # specify the ranges
 beta  <- 0.4  
 # eta_w <- seq(0,1, length.out=5) 
 eta_t <- seq(0.001,0.5, length.out=n_out) #0.001 
 rho     <- seq(0,0.01, length.out=n_in)
 omega <- seq(0.001,1 , length.out=n_in) #note omega must be > 0, was 0.1
 s <- seq(1,2,length.out=n_out)
